---
title: "Multi Attribute Decision Making in R"
output: html_notebook
---




# Read in data
```{r}
DM <- data.frame(cost=as.numeric(runif(5,100, 200)),                                   #cost attribute, 100-200
                 productivity=as.numeric(abs(rnorm(5))),                               #benefit attribute, abs(normalDist)
                 location=as.numeric(floor(runif(5, 0, 5))),                           #benefit attribute, 0-5
                 row.names = sprintf("alternative_%d",seq(1:5))
      )
w <- data.frame(t(matrix(c(0.45, 0.35, 0.2))))
names(w) <- names(DM)
DM <- rbind(w,DM)
row.names(DM)[1] = "weights"
DM
```

# Weight Vector Normalize
```{r}

weightVectorNormalize <- function(DM){
  VNDM <- DM
  for (i in 1:ncol(DM)){
  
      denom <- sqrt(sum(DM[,i]^2))
      
      for(j in 2:length(DM[,i])){
        
        VNDM[j,i] <- DM[1,i]*((DM[j,i])/denom)
      }
  }
  return(VNDM)
}

VNDM <- weightVectorNormalize(DM)
VNDM
```

# Capture Positive and Negative Ideal
```{r}

PNI <- function(DM){
  s <- data.frame(row.names=FALSE)
  for (name in names(DM)){
      p<-0
      n<-0
      if(grepl("cost", name)){
         # min is better
         p <- min(DM[2:nrow(DM),name])         #remember to ignore the weight row
         n <- max(DM[2:nrow(DM),name])         #remember to ignore the weight row
         #cat(name, "neg:",n,"\tpos:",p,"\n")
      }
      else{
         # max is better
         p <- max(DM[2:nrow(DM),name])         #remember to ignore the weight row
         n <- min(DM[2:nrow(DM),name])         #remember to ignore the weight row
         #cat(name, "neg:",n,"\tpos:",p,"\n")
      }
      
      s <- rbind(s,t(data.frame(c(name, p, n))))
  }
  
  # Structure labeling
  names(s) <- c("Name", "PositiveIdeal", "NegativeIdeal")
  row.names(s) <- names(DM)
  
  # Structure & Convert data
  d <- data.frame(t(s[,2:ncol(s)]))
  d2 <- data.frame(apply(d, 2, as.numeric))
  
  # Re-structure labeling
  names(d2) <- names(d)
  row.names(d2) <- row.names(d)
  
  return(d2)
}
ideals <- PNI(VNDM)
ideals
```

# Get S Vectors (Distances of each alternative to the PNI)
```{r}
distanceFromIdeals <- function(ideals, DM){
  SPlus <- c()
  SMinus <- c()
  for(i in 2:nrow(DM)){
    SPlus[i] <- sqrt(sum((DM[i,] - ideals[1,])^2))
    SMinus[i] <- sqrt(sum((DM[i,] - ideals[2,])^2))
  }
  return (data.frame(SPlus, SMinus))
}

S <- distanceFromIdeals(ideals, VNDM)
row.names(S) <- row.names(VNDM)
S

```

# Calculate the C*, distance of how far this alternatives distance was from the 
# negative ideal, and how close it was to the positive ideal
# C* = SMinus/ (SMinus - SPlus)

```{r}
CStar <- data.frame(S[,2] / (S[,1]-S[,2]))
names(CStar) <- "C*"
row.names(CStar) <- row.names(VNDM)
CStar
```

# In conclusion, we would select the first alternative, because he has the best score